Music Perception 2: Analysis

### 2022-01-31 experiment-1/analysis/analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Articulation (***)
```{r, echo = TRUE}
# normality check
ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
ioi_art_norm_judge <- shapiro.test(ioi[Skill == "articulation"]$Mean)

@@

qqnorm(ioi[Skill == "articulation"]$Mean)
qqline(ioi[Skill == "articulation"]$Mean)
ioi_art_norm_judge

@@

## Dynamics (**)
```{r, echo = TRUE}
# normality check
ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
ioi_dyn_norm_judge <- shapiro.test(ioi[Skill == "dynamics"]$Mean)

@@

qqnorm(ioi[Skill == "dynamics"]$Mean)
qqline(ioi[Skill == "dynamics"]$Mean)
ioi_dyn_norm_judge

@@

## Articulation (***)
```{r, echo = TRUE}
# normality check
ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
ioi_art_tra_norm_judge <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)

@@

qqnorm(ioi_tra[Skill == "articulation"]$Mean)
qqline(ioi_tra[Skill == "articulation"]$Mean)
ioi_art_tra_norm_judge

@@

## Dynamics (**)
```{r, echo = TRUE}
# normality check
ioi_dyn_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
ioi_dyn_tra_norm_judge <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)

@@

qqnorm(ioi_tra[Skill == "dynamics"]$Mean)
qqline(ioi_tra[Skill == "dynamics"]$Mean)
ioi_dyn_tra_norm_judge

@@

ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
## Articulation (n.s.)
```{r, echo = TRUE}
# normality check
cv_art_norm_teaching <- shapiro.test(cv[Skill == "articulation"]$Teaching)
cv_art_norm_judge <- shapiro.test(cv[Skill == "articulation"]$CV)

@@

qqnorm(cv[Skill == "articulation"]$CV)
qqline(cv[Skill == "articulation"]$CV)
cv_art_norm_judge

@@

## Dynamics (n.s.)
```{r, echo = TRUE}
# normality check
cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
cv_dyn_norm_judge <- shapiro.test(cv[Skill == "dynamics"]$CV)

@@

qqnorm(cv[Skill == "dynamics"]$CV)
qqline(cv[Skill == "dynamics"]$CV)
cv_dyn_norm_judge

@@

## Legato (**)
```{r, echo = TRUE}
# normality check
kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
kot_leg_norm_judge <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)

@@

qqnorm(kot_all[Subcomponent == "Legato"]$Mean)
qqline(kot_all[Subcomponent == "Legato"]$Mean)
kot_leg_norm_judge

@@

## Staccato (***)
```{r, echo = TRUE}
# normality check
kot_sta_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
kot_sta_norm_judge <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)

@@

qqnorm(kot_all[Subcomponent == "Staccato"]$Mean)
qqline(kot_all[Subcomponent == "Staccato"]$Mean)
kot_sta_norm_judge

@@

## Forte (n.s.)
```{r, echo = TRUE}
# normality check
kot_for_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
kot_for_norm_judge <- shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)

@@

qqnorm(kot_all[Subcomponent == "Forte"]$Mean)
qqline(kot_all[Subcomponent == "Forte"]$Mean)
kot_for_norm_judge

@@

## Piano (n.s.)
```{r, echo = TRUE}
# normality check
kot_pia_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
kot_pia_norm_judge <- shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)

@@

qqnorm(kot_all[Subcomponent == "Piano"]$Mean)
qqline(kot_all[Subcomponent == "Piano"]$Mean)
kot_pia_norm_judge

@@

## Forte (***)
```{r, echo = TRUE}
# normality check
vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
vel_for_norm_judge <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Forte"]$Mean)
qqline(vel_all[Subcomponent == "Forte"]$Mean)
vel_for_norm_judge

@@

## Piano (n.s.)
```{r, echo = TRUE}
# normality check
vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
vel_pia_norm_judge <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Piano"]$Mean)
qqline(vel_all[Subcomponent == "Piano"]$Mean)
vel_pia_norm_judge

@@

## Legato (n.s.)
```{r, echo = TRUE}
# normality check
vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
vel_leg_norm_judge <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Legato"]$Mean)
qqline(vel_all[Subcomponent == "Legato"]$Mean)
vel_leg_norm_judge

@@

## Staccato (n.s.)
```{r, echo = TRUE}
# normality check
vel_sta_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
vel_sta_norm_judge <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Staccato"]$Mean)
qqline(vel_all[Subcomponent == "Staccato"]$Mean)
vel_sta_norm_judge

@@

## Forte to Piano (***)
```{r, echo = TRUE}
# normality check
vel_diff_ftop_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
vel_diff_ftop_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Mean)
qqline(vel_diff_all[Subcomponent == "FtoP"]$Mean)
vel_diff_ftop_norm_judge

@@

## Piano to Forte (***)
```{r, echo = TRUE}
# normality check
vel_diff_ptof_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
vel_diff_ptof_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Mean)
qqline(vel_diff_all[Subcomponent == "PtoF"]$Mean)
vel_diff_ptof_norm_judge

@@

## Legato to Staccato (n.s.)
```{r, echo = TRUE}
# normality check
vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
vel_diff_ltos_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Mean)
qqline(vel_diff_all[Subcomponent == "LtoS"]$Mean)
vel_diff_ltos_norm_judge

@@

## Staccato to Legato (n.s.)
```{r, echo = FALSE}
# normality check
vel_diff_stol_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
vel_diff_stol_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "StoL"]$Mean)
qqline(vel_diff_all[Subcomponent == "StoL"]$Mean)
vel_diff_stol_norm_judge

>>>>

## Articulation (***)
```{r, echo = TRUE}
# normality check
ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
ioi_art_norm_performance <- shapiro.test(ioi[Skill == "articulation"]$Mean)

@@

qqnorm(ioi[Skill == "articulation"]$Mean)
qqline(ioi[Skill == "articulation"]$Mean)
ioi_art_norm_performance

@@

## Dynamics (**)
```{r, echo = TRUE}
# normality check
ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)

@@

qqnorm(ioi[Skill == "dynamics"]$Mean)
qqline(ioi[Skill == "dynamics"]$Mean)
ioi_dyn_norm_performance

@@

## Articulation (***)
```{r, echo = TRUE}
# normality check
ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
ioi_art_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)

@@

qqnorm(ioi_tra[Skill == "articulation"]$Mean)
qqline(ioi_tra[Skill == "articulation"]$Mean)
ioi_art_tra_norm_performance

@@

## Dynamics (**)
```{r, echo = TRUE}
# normality check
ioi_dyn_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
ioi_dyn_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)

@@

qqnorm(ioi_tra[Skill == "dynamics"]$Mean)
qqline(ioi_tra[Skill == "dynamics"]$Mean)
ioi_dyn_tra_norm_performance

@@

ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

## Articulation (n.s.)
```{r, echo = TRUE}
# normality check
cv_art_norm_teaching <- shapiro.test(cv[Skill == "articulation"]$Teaching)
cv_art_norm_performance <- shapiro.test(cv[Skill == "articulation"]$CV)

@@

qqnorm(cv[Skill == "articulation"]$CV)
qqline(cv[Skill == "articulation"]$CV)
cv_art_norm_performance

@@

## Dynamics (n.s.)
```{r, echo = TRUE}
# normality check
cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
cv_dyn_norm_performance <- shapiro.test(cv[Skill == "dynamics"]$CV)

@@

qqnorm(cv[Skill == "dynamics"]$CV)
qqline(cv[Skill == "dynamics"]$CV)
cv_dyn_norm_performance

@@

## Legato (**)
```{r, echo = TRUE}
# normality check
kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
kot_leg_norm_performance <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)

@@

qqnorm(kot_all[Subcomponent == "Legato"]$Mean)
qqline(kot_all[Subcomponent == "Legato"]$Mean)
kot_leg_norm_performance

@@

## Staccato (***)
```{r, echo = TRUE}
# normality check
kot_sta_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
kot_sta_norm_performance <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)

@@

qqnorm(kot_all[Subcomponent == "Staccato"]$Mean)
qqline(kot_all[Subcomponent == "Staccato"]$Mean)
kot_sta_norm_performance

@@

## Forte (n.s.)
```{r, echo = TRUE}
# normality check
kot_for_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
kot_for_norm_performance <- shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)

@@

qqnorm(kot_all[Subcomponent == "Forte"]$Mean)
qqline(kot_all[Subcomponent == "Forte"]$Mean)
kot_for_norm_performance

@@

## Piano (n.s.)
```{r, echo = TRUE}
# normality check
kot_pia_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
kot_pia_norm_performance <- shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)

@@

qqnorm(kot_all[Subcomponent == "Piano"]$Mean)
qqline(kot_all[Subcomponent == "Piano"]$Mean)
kot_pia_norm_performance

@@

## Forte (***)
```{r, echo = TRUE}
# normality check
vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
vel_for_norm_performance <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Forte"]$Mean)
qqline(vel_all[Subcomponent == "Forte"]$Mean)
vel_for_norm_performance

@@

## Piano (n.s.)
```{r, echo = TRUE}
# normality check
vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
vel_pia_norm_performance <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Piano"]$Mean)
qqline(vel_all[Subcomponent == "Piano"]$Mean)
vel_pia_norm_performance

@@

## Legato (n.s.)
```{r, echo = TRUE}
# normality check
vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
vel_leg_norm_performance <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Legato"]$Mean)
qqline(vel_all[Subcomponent == "Legato"]$Mean)
vel_leg_norm_performance

@@

## Staccato (n.s.)
```{r, echo = TRUE}
# normality check
vel_sta_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
vel_sta_norm_performance <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Staccato"]$Mean)
qqline(vel_all[Subcomponent == "Staccato"]$Mean)
vel_sta_norm_performance

@@

## Forte to Piano (***)
```{r, echo = TRUE}
# normality check
vel_diff_ftop_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
vel_diff_ftop_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Mean)
qqline(vel_diff_all[Subcomponent == "FtoP"]$Mean)
vel_diff_ftop_norm_performance

@@

## Piano to Forte (***)
```{r, echo = TRUE}
# normality check
vel_diff_ptof_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
vel_diff_ptof_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Mean)
qqline(vel_diff_all[Subcomponent == "PtoF"]$Mean)
vel_diff_ptof_norm_performance

@@

## Legato to Staccato (n.s.)
```{r, echo = TRUE}
# normality check
vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
vel_diff_ltos_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Mean)
qqline(vel_diff_all[Subcomponent == "LtoS"]$Mean)
vel_diff_ltos_norm_performance

@@

## Staccato to Legato (n.s.)
```{r, echo = FALSE}
# normality check
vel_diff_stol_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
vel_diff_stol_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "StoL"]$Mean)
qqline(vel_diff_all[Subcomponent == "StoL"]$Mean)
vel_diff_stol_norm_performance

### 2022-01-31 experiment-2/analysis/analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Articulation (n.s.)
```{r, echo = FALSE}
# normality check
ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
ioi_art_norm_judge <- shapiro.test(ioi[Skill == "articulation"]$Mean)

@@

## Dynamics (n.s.)
```{r, echo = FALSE}
# normality check
ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
ioi_dyn_norm_judge <- shapiro.test(ioi[Skill == "dynamics"]$Mean)

@@

## Articulation (n.s.)
```{r, echo = FALSE}
# normality check
ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
ioi_art_tra_norm_judge <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)

@@

## Dynamics (*)
```{r, echo = FALSE}
# normality check
ioi_dyn_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
ioi_dyn_tra_norm_judge <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)

@@

## Articulation (n.s.)
```{r, echo = FALSE}
# normality check
cv_art_norm_teaching <- shapiro.test(cv[Skill == "articulation"]$Teaching)
cv_art_norm_judge <- shapiro.test(cv[Skill == "articulation"]$CV)

@@

## Dynamics (n.s.)
```{r, echo = FALSE}
# normality check
cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
cv_dyn_norm_judge <- shapiro.test(cv[Skill == "dynamics"]$CV)

@@

## Legato (n.s.)
```{r, echo = FALSE}
# normality check
kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
kot_leg_norm_judge <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)

@@

## Staccato (n.s.)
```{r, echo = FALSE}
# normality check
kot_sta_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
kot_sta_norm_judge <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)

@@

## Forte (n.s.)
```{r, echo = FALSE}
# normality check
kot_for_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
kot_for_norm_judge <- shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)

@@

## Piano (*)
```{r, echo = FALSE}
# normality check
kot_pia_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
kot_pia_norm_judge <- shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)

@@

## Forte (**)
```{r, echo = FALSE}
# normality check
vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
vel_for_norm_judge <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)

@@

## Piano (*)
```{r, echo = FALSE}
# normality check
vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
vel_pia_norm_judge <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)

@@

cor_vel_pia_spearman <- cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
cor_vel_pia_spearman
```
## Legato (n.s.)
```{r, echo = FALSE}
# normality check
vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
vel_leg_norm_judge <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)

@@

## Staccato (n.s.)
```{r, echo = FALSE}
# normality check
vel_sta_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
vel_sta_norm_judge <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)

@@

## Forte to Piano (***)
```{r, echo = FALSE}
# normality check
vel_diff_ftop_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
vel_diff_ftop_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)

@@

## Piano to Forte (***)
```{r, echo = FALSE}
# normality check
vel_diff_ptof_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
vel_diff_ptof_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)

@@

cor_vel_diff_ptof_spearman <- cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean, method = "spearman", exact = FALSE)
cor_vel_diff_ptof_spearman
```
## Legato to Staccato (n.s.)
```{r, echo = FALSE}
# normality check
vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
vel_diff_ltos_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)

@@

## Staccato to Legato (*)
```{r, echo = FALSE}
# normality check
vel_diff_stol_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
vel_diff_stol_norm_judge <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)

>>>>

## Articulation (n.s.)
```{r, echo = FALSE}
# normality check
ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
ioi_art_norm_performance <- shapiro.test(ioi[Skill == "articulation"]$Mean)

@@

## Dynamics (n.s.)
```{r, echo = FALSE}
# normality check
ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)

@@

## Articulation (n.s.)
```{r, echo = FALSE}
# normality check
ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
ioi_art_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)

@@

## Dynamics (*)
```{r, echo = FALSE}
# normality check
ioi_dyn_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
ioi_dyn_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)

@@

## Articulation (n.s.)
```{r, echo = FALSE}
# normality check
cv_art_norm_teaching <- shapiro.test(cv[Skill == "articulation"]$Teaching)
cv_art_norm_performance <- shapiro.test(cv[Skill == "articulation"]$CV)

@@

## Dynamics (n.s.)
```{r, echo = FALSE}
# normality check
cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
cv_dyn_norm_performance <- shapiro.test(cv[Skill == "dynamics"]$CV)

@@

## Legato (n.s.)
```{r, echo = FALSE}
# normality check
kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
kot_leg_norm_performance <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)

@@

## Staccato (n.s.)
```{r, echo = FALSE}
# normality check
kot_sta_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
kot_sta_norm_performance <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)

@@

## Forte (n.s.)
```{r, echo = FALSE}
# normality check
kot_for_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
kot_for_norm_performance <- shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)

@@

## Piano (*)
```{r, echo = FALSE}
# normality check
kot_pia_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
kot_pia_norm_performance <- shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)

@@

## Forte (**)
```{r, echo = FALSE}
# normality check
vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
vel_for_norm_performance <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)

@@

## Piano (*)
```{r, echo = FALSE}
# normality check
vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
vel_pia_norm_performance <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)

@@

cor_vel_pia_spearman <- cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
cor_vel_pia_spearman
```
## Legato (n.s.)
```{r, echo = FALSE}
# normality check
vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
vel_leg_norm_performance <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)

@@

## Staccato (n.s.)
```{r, echo = FALSE}
# normality check
vel_sta_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
vel_sta_norm_performance <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)

@@

## Forte to Piano (***)
```{r, echo = FALSE}
# normality check
vel_diff_ftop_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
vel_diff_ftop_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)

@@

## Piano to Forte (***)
```{r, echo = FALSE}
# normality check
vel_diff_ptof_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
vel_diff_ptof_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)

@@

cor_vel_diff_ptof_spearman <- cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean, method = "spearman", exact = FALSE)
cor_vel_diff_ptof_spearman
```
## Legato to Staccato (n.s.)
```{r, echo = FALSE}
# normality check
vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
vel_diff_ltos_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)

@@

## Staccato to Legato (*)
```{r, echo = FALSE}
# normality check
vel_diff_stol_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
vel_diff_stol_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)
